Eviction and Crime: Evidence from Boston

### 2023-04-12 writing/paper/main.tex

        \begin{figure}
            \centering
            \includegraphics{research/institutional_context/sources/map_of_where_court_sits_-_jan_2019.pdf}
            \caption{Divisions of the Massachusetts Housing Court}
        \end{figure}

@@

        After the length of time specified by the notice to quit has passed \footnote{If the notice to quit was for nonpayment of rent, the specified length of time must pass without curing of the nonpayment by the tenant.}, the tenant's rental agreement has ended. To continue with the eviction, the landlord is required to hire a local law enforcement officer to serve the tenant with a \textit{summary process summons and complaint}. Massachusetts law says that the summary process summons and complaint must then be filed with the court on a Monday between seven and 30 days after it was served. The date on which the summons and complaint is filed with the court is known as the \textit{entry date}. If a landlord fails to follow any of the above protocol—say, by serving a notice to quit that specifies too short of a time period or by failing to deliver a summary process summons and complaint to the tenant—her case may be dismissed, automatically awarding victory to the tenant.

@@

\section{Empirical Strategy: Difference-in-Differences}
    I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties. I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.

>>>>

\begin{landscape}

        \begin{figure}
            \centering
            \includegraphics[scale=0.75]{research/institutional_context/sources/map_of_where_court_sits_-_jan_2019.pdf}
            \caption{Divisions of the Massachusetts Housing Court \citep{housing_court_4_all_housing_nodate}}
        \end{figure}
\end{landscape}

@@

        After the length of time specified by the notice to quit has passed \footnote{If the notice to quit was for nonpayment of rent, the specified length of time must pass without curing of the nonpayment by the tenant.}, the tenant's rental agreement has ended. To continue with the eviction, the landlord is required to hire a local law enforcement officer to serve the tenant with a \textit{summary process summons and complaint}. Massachusetts law says that the landlord must then file the summary process complaint with the court on a Monday between seven and 30 days after it was served. The date on which the summons and complaint is filed with the court is known as the \textit{entry date}. If a landlord fails to follow any of the above protocol—say, by serving a notice to quit that specifies too short of a time period or by failing to deliver a summary process summons and complaint to the tenant—her case may be dismissed, automatically awarding victory to the tenant.

        Upon receiving the summons and complaint, the tenant may file a Summary Process Answer form with the court. This is the tenant's opportunity to provide \textit{defenses}, or legal reasons that the landlord should not evict the tenant, and \textit{counterclaims}, or claims that the tenant has against the landlord. The tenant may also file for \textit{discovery} at this stage. Discovery is the process by which the tenant may request information from her landlord, which the landlord must provide under oath. Tenants often use discovery as a means of postponing a trial: as long as the court receives the request for discovery before mediation begins, the eviction process is halted by two weeks.

        Once the summons and complaint has been filed with the court, the tenant has had a chance to answer, and the discovery process is finished, mediation begins. Housing specialists facilitate mediation with the goal of avoiding a trial by producing a legally binding agreement acceptable for both the tenant and the landlord. Mediation is confidential—matters discussed during mediation may not go before a judge.

        If mediation does not result in an agreement between the landlord and the tenant, a trial is held in front of a judge, who rules in favor of the landlord, the plaintiff, or the tenant, the defendant. If the judge rules in favor of the tenant, the eviction process has concluded. If the judge rules in favor of the landlord, then the tenant has ten days after the judgment to appeal the case. After the tenth day, the landlord may obtain an \textit{execution for possession} from the court. For the next 90 days, the landlord may hire a law enforcement officer to force a tenant to leave the property with 48 hours notice.

@@

\section{Empirical Strategy: Difference-in-Differences}
    \subsection{Conceptualizing Treatment}
    I seek to estimate the average treatment effects of plaintiff victory in eviction cases on treated properties. I use the staggered difference-in-difference estimator proposed in \cite{callaway_difference--differences_2021}, which uses two-period, two-unit difference-in-difference estimators to estimate time- and cohort-specific ATTs and then aggregates them, weighting by cohort size, to produce summaries of the ATT.
